Working title: Ecological network control

### 2018-05-24 paper/manuscript.Rmd
Refs from manuscript to supp info are now in parenthesis to improve flow

Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing. 
A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constrain: an applicant can be assigned to at most one position and visceversa.
Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
At first glance, however, is  hard to identify how exactlty matchings are related to structural controllability. 
The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left). 
We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions. 
The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control input should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).

@@

The technical details of the algorithm we use to find a maximum matching in a network can be found in the supplementary information section \@ref(S-one-maximum-matching).

@@

After finding the minimum driver node set in each of our networks we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
We therefore use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995]. 
These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor). In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way; further details about this procedure can be found in the supplementary information section \@ref(S-randomisations).

>>>>

Maximum matching is a widely studied topic in graph theory and is commonly used in multiple applications, ranging from dating apps and wireless communications to organ transplant allocation and peer to peer file sharing. 
A matching in an unweighted directed graph is defined as a set of links that do not share a common start or end nodes; the largest possible matching is called maximum matching. 
For example, in a network composed by jobs and job applicants, a matching is any pairing between applicants and positions that satisfies one basic constrain: an applicant can be assigned to at most one position and visceversa.
Consequently, a maximum matching is an optimal pairing, one that maximises the number of applicants with jobs and the number of positions filled. 
At first glance, however, is  hard to identify how exactlty matchings are related to structural controllability. 
The key is to note that the conditions of structural controllability imply that, just like the one to one relationship between jobs and applicants, there needs to be a one to one relationship between *superior* and *subordinate* nodes (Figure \@ref(fig:fig-example-networks)b, bottom left). 
We use the maximum matching algorithm to find an optimal pairing of superior and subordinate nodes in a way consistent with the controllability conditions (supplementary information section \@ref(S-one-maximum-matching)). 
The result is that a matching can actually be decomposed into a set of paths that reveal how a control signal can flow across the links in a network to reach every node that compose it. 
And so, as recently shown [@liu_controllability_2011], the minimum driver node set, those to which an external control input should be applied to make the system controllable, corresponds exactly to the *unmatched* nodes in the network (Figure \@ref(fig:fig-control-configuration)).

@@

@@

After finding the minimum driver node set in each of our networks we want to test whether invasion status or other predictors are correlated to this metric of controllability. 
We therefore use a set of generalised linear models (with binomial error structure) to investigate the effect of invasion status while also including covariates related to species richness, since one might naively expect to see a negative relationship between richness and controllability [@menge_indirect_1995]. 
These covariates included the total number of species, plant richness, pollinators richness, the ratio of plant to pollinator richness, the link density (connectance), and the study site (as a two-level factor). 
In addition, we also explored whether real networks differ in their architecture from random ones in a concerted way (supplementary information section \@ref(S-randomisations)).
